The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Finalzie Zwitter comments. Closes #28

We inferred labels for all \rave\ spectra using this main-sequence/sub-giant star model.  \stub{from Zwitter: ensure it is clear that we say we are running this model on all spectra}
The results for the survey sample are shown in the centre panel of Figure \ref{fig:test-set-density}.  
The increased density of solar-type stars is consistent with \rave\
observing stars in the local neighbourhood, and the high number of turn-off
and main-sequence stars relative to the sub-giant branch is expected from 
the relative lifetimes of these evolutionary phases.  An over-density
of stars near the base of the giant branch is also present.  This artefact is due 
to having giant stars in the test set, but not in the training set, and the
model is (poorly) extrapolating outside the convex hull of the training set.

@@

Similar to Sections \ref{sec:a-simple-model} and \ref{sec:unevolved-star-model},
we used a quadratic vectorizer for the giant star model.  Here the terms are 
expanded in the same way as equation \ref{eq:vectorizer-three-label}, only
with nine labels instead of three.  We set the regularization hyperparameter $\Lambda$
in the same way described in Section \ref{sec:unevolved-star-model}, using the same 30 trials of $\Lambda$.
The results are shown in Figure \ref{fig:set-hyperparameters}, where
again the enveloped region represents the minimum and maximum change in RMS label
deviation with respect to the unregularized case.  At the point of maximum improvement 
near $\Lambda = 0.13$ $(\approx10^{-0.9})$, the RMS in all nine labels has decreased by up to $30$\%,
with all labels showing an improvement $>5$\%, and the mean improvement over all labels is about 10\%.
Near $\Lambda \approx 10^{-0.9}$ to $10^{-0.3}$, the regularization also produces a sparser matrix
of $\vectheta$, with $\approx20$\% more terms (mostly cross-terms) having zero-valued entries.
Based on the increased model sparsity and decreasing RMS deviation in the labels, 
we adopt $\Lambda = 0.57$ ($10^{-0.25}$) for the giant star model.  The bias in 
labels from a regularized model with $\Lambda = 0.57$ is negligible: $-0.3$~K in 
$\teff$, and $<$0.007~dex in magnitude for $\logg$ and all seven elements.  The RMS
at this regularization strength is 69~K in $\teff$, 0.18~dex in $\logg$, and varies
between $0.07-0.09$~dex depending on the elemental abundance.  We inferred labels 
for all \Nspectra\ \rave\ spectra using this model, and these results are summarized in
the right panel of Figure \ref{fig:test-set-density}.  The red clump is clearly visible
and in the expected location, without requiring any post-analysis calibration.
However, artefacts due to dwarf stars in the test set are also present.

>>>>

We inferred labels for all \Nspectra\ \rave\ spectra using this main-sequence/sub-giant
star model; we made no \emph{a priori} decisions as to whether a star was likely a
main-sequence/sub-giant star or not.  The results for the entire survey sample are shown
in the centre panel of Figure \ref{fig:test-set-density}.  The increased density of 
solar-type stars is consistent with \rave\ observing stars in the local neighbourhood, 
and the high number of turn-off and main-sequence stars relative to the sub-giant branch 
is expected from the relative lifetimes of these evolutionary phases.  An over-density
of stars near the base of the giant branch is also present.  This artefact is due 
to having giant stars in the test set, but not in the training set, and the model is 
(poorly) extrapolating outside the convex hull of the training set.

@@

Similar to Sections \ref{sec:a-simple-model} and \ref{sec:unevolved-star-model},
we used a quadratic vectorizer for the giant star model.  Here the terms are 
expanded in the same way as equation \ref{eq:vectorizer-three-label}, only
with nine labels instead of three.  We set the regularization hyperparameter $\Lambda$
in the same way described in Section \ref{sec:unevolved-star-model}, using the same 30 trials of $\Lambda$.
The results are shown in Figure \ref{fig:set-hyperparameters}, where
again the enveloped region represents the minimum and maximum change in RMS label
deviation with respect to the unregularized case.  At the point of maximum improvement 
near $\Lambda = 0.13$ $(\approx10^{-0.9})$, the RMS in all nine labels has decreased by up to $30$\%,
with all labels showing an improvement $>5$\%, and the mean improvement over all labels is about 10\%.
Near $\Lambda \approx 10^{-0.9}$ to $10^{-0.3}$, the regularization also produces a sparser matrix
of $\vectheta$, with $\approx20$\% more terms (mostly cross-terms) having zero-valued entries.
Based on the increased model sparsity and decreasing RMS deviation in the labels, 
we adopt $\Lambda = 0.57$ ($10^{-0.25}$) for the giant star model.  The bias in 
labels from a regularized model with $\Lambda = 0.57$ is negligible: $-0.3$~K in 
$\teff$, and $<$0.007~dex in magnitude for $\logg$ and all seven elements.  The RMS
at this regularization strength is 69~K in $\teff$, 0.18~dex in $\logg$, and varies
between $0.07-0.09$~dex depending on the elemental abundance.

We inferred labels for all \Nspectra\ \rave\ spectra using this model, again without
regard for whether a star was likely a giant or not.  The results for all survey stars
are summarized in the right panel of Figure \ref{fig:test-set-density}.  The red clump
is clearly visible and in the expected location, without requiring any post-analysis 
calibration.  However, artefacts due to dwarf stars being present in the test set,
and not in the training set, are also present.
